Causes and effects in Dichotomous Comparative Judgments: an information-theoretical system of plausible mechanism

### 2024-08-01 index.qmd
section:background,dag; process:write;figures

![Two unconnected nodes](images/figures/dag_bb1.png){#fig-dag_bb1 fig-align="center" width=40%}

![Two connected nodes or descendant](images/figures/dag_bb2.png){#fig-dag_bb2 fig-align="center" width=40%}

![Chain or pipe](images/figures/dag_bb3.png){#fig-dag_bb3 fig-align="center" width=100%}

![Fork](images/figures/dag_bb4.png){#fig-dag_bb4 fig-align="center" width=100%}

![Collider or inmorality](images/figures/dag_bb5.png){#fig-dag_bb5 fig-align="center" width=100%}

>>>>

![Two unconnected nodes](images/figures/dag_bb1.png){#fig-dag_bb1 fig-align="center" width=30%}

![Two connected nodes or descendant](images/figures/dag_bb2.png){#fig-dag_bb2 fig-align="center" width=30%}

![Chain or pipe](images/figures/dag_bb3.png){#fig-dag_bb3 fig-align="center" width=85%}

![Fork](images/figures/dag_bb4.png){#fig-dag_bb4 fig-align="center" width=85%}

![Collider or inmorality](images/figures/dag_bb5.png){#fig-dag_bb5 fig-align="center" width=85%}
